---
title: "Analysis of open policing data in `r params$year`"
output: pdf_document 
params:
  year: 2018
---

On a typical day in the United States, police officers make more than 50,000 traffic stops. Our team is gathering, analyzing, and releasing records from millions of traffic stops by law enforcement agencies across the country. Our goal is to help researchers, journalists, and policymakers investigate and improve interactions between police and the public.

```{r, include=FALSE}
library(data.table)
library(ggplot2)
library(DBI)
library(dplyr)

theme_set(theme_minimal())

plot_prop <- function(df, var) {
  df |> 
  mutate(subject_race = forcats::fct_reorder(subject_race, -{{ var }})) |> 
  ggplot(aes(subject_race, {{ var }})) + 
    geom_col(aes(fill = subject_race)) +
    geom_text(aes(label = scales::label_percent()({{ var }})), vjust = -0.5) + 
    scale_y_continuous(labels = scales::label_percent()) + 
    scale_fill_brewer(palette = "PuBuGn", direction = -1, name = NULL) + 
    theme(legend.position = "top",
          axis.title = element_blank()) 
}

ymisc::set_knitr_options(echo = FALSE)

con <- DBI::dbConnect(RMySQL::MySQL(),
                      host   = "localhost",
                      dbname = "stanford_policing",
                      user      = "root",
                      password  = "",
                      port     = 3306)

year <- params$year
race <- params$race

s <- glue::glue("
SELECT t2.subject_race, type, arrest_made, citation_issued, warning_issued, violation,
        frisk_performed, search_conducted 
FROM (SELECT 
	raw_row_number,
	type, 
  arrest_made,
  citation_issued, 
  warning_issued, 
  violation, 
  frisk_performed,
  search_conducted 
FROM after_stop_actions) t1 INNER JOIN (
  SELECT raw_row_number, subject_race
  FROM persons_info
) t2 ON t1.raw_row_number = t2.raw_row_number 
  INNER JOIN (
    SELECT distinct raw_row_number 
    FROM stops_info 
    WHERE EXTRACT(year FROM date) = {year}
) t3 ON t2.raw_row_number = t3.raw_row_number
")

ret = as.data.table(dbGetQuery(con, s))
```


```{r}
props <- ret[subject_race != "NA", .(
  arrest_prop = sum(ifelse(arrest_made == "TRUE", 1, 0)) / .N,
  citation_prop = sum(ifelse(citation_issued == "TRUE", 1, 0)) / .N,
  warning_prop = sum(ifelse(warning_issued == "TRUE", 1, 0)) / .N,
  frisk_prop = sum(ifelse(frisk_performed == "TRUE", 1, 0)) / .N, 
  search_prop = sum(ifelse(search_conducted == "TRUE", 1, 0)) / .N
), subject_race]
```


Here is your report of some racial statistics 

## Arrest proportions 

```{r}
plot_prop(props, arrest_prop)
```

## Citation proportion 

```{r}
plot_prop(props, citation_prop)
```

## Warning proportion 

```{r}
plot_prop(props, warning_prop)
```

## Frisk propotion

```{r}
plot_prop(props, frisk_prop)
```

## Search proportion 

```{r}
plot_prop(props, search_prop)
```
